Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-05 paper/galsize_paper.tex
Updated intro

In the $\lcdm$ framework of cosmological structure formation, galaxies form at the centers of dark matter halos. Highly complex and nonlinear baryonic processes regulate galaxy formation, and the quest for a fine-grained understanding of these processes is one of the chief goals of theoretical astrophysics today.

Observationally, many properties of observed galaxies exhibit remarkably tight scaling relations. Among the most fundamental of these relations is the strong correlation between galaxy size and stellar mass and luminosity. The scaling of galaxy size with galaxy mass is well-measured in the local Universe \citep{shen_etal03,guo_etal09,huang_etal13,zhang_yang17} and at high-redshift \citep{trujillo_etal04,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,lange_etal15,huang_etal17}.

These well-measured scaling relations are challenging to faithfully recover using ab initio galaxy formation methods such as hydrodynamical simulations and semi-analytic models, and provide useful boundary conditions for the calibration of such modeling efforts \citep{khochfar_silk06,dutton_etal10,hopkins_etal10a,bottrell_etal17b}. The precision cosmology program also depends critically on accurate modeling of galaxies, so that cosmological parameter inference can be confidently conducted without undue interference from uncertainty in baryonic physics \citep{LSST_science,LSST_galaxies}.

@@

>>>>

Many properties of observed galaxies exhibit remarkably tight scaling relations. Galaxy size, typically quantified by a half-mass or half-light radius, $\rhalf,$ has well-measured scaling with galaxy mass $\mstar$ in the local Universe \citep{shen_etal03,guo_etal09,huang_etal13,lange_etal15,zhang_yang17}, and at higher redshift \citep{trujillo_etal04,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,huang_etal17}. Observational constraints on models for galaxy $\rhalf$ typically come from one-point function measurements such as $\median{\rhalf}{\mstar}$ and $\sigma(\rhalf\vert\mstar),$ e.g.,  \citet{khochfar_silk06,desmond_etal17,bottrell_etal17b,hou_etal17,somerville_etal17}, or otherwise from catalogs of galaxy groups \citep{weinmann_etal08,huertas_company_etal13b,spindler_wake17}. Observations of two-point galaxy clustering, $\wproj(\rproj),$ have historically been used to place tight constraints on many features of the galaxy--halo connection, such as its $\mstar-$dependence \citep{moster_etal10,leauthaud_etal11,reddick_etal13,skibba_etal15}, dependence on luminosity \citep{tinker_etal05,cacciato_etal13}, broadband color \citep{coil_etal08,zehavi_etal11,guo_etal11,hearin_watson13}, and star-formation rate \citep{wang_etal07,tinker_etal13,watson_etal14}. In the present work, we exploit the constraining power of $\wproj(\rproj)$ to test empirical models connecting galaxy $\mstar$ and $\rhalf$ to the properties of the galaxy's parent dark matter halo.

@@

%The precision cosmology program also depends critically on accurate modeling of galaxies, so that cosmological parameter inference can be confidently conducted without undue interference from uncertainty in baryonic physics \citep{LSST_science,LSST_galaxies}.
